### 2021-05-17 manuscript/v8_submission_finalization/assignment_files/manuscript_tex4submission.tex
assignment files

@@

>>>>

A recent review on COVID-19 based on evidence from the US and UK concludes that low socio-economic status groups are being hit harder by the pandemic \cite{Wachtler2020Socioeconomic}. Albeit specific pathways remain unclear, many studies found associations with poverty or its correlates such as poor and potentially overcrowded housing conditions. For Germany, a higher case fatality of COVID-19 cases in districts with higher socio-economic deprivation has also been reported just recently, which was especially pronounced in the second wave of the pandemic \cite{DAE218459}. Similarly, our analysis identified a decreasing effect on COVID-19 case numbers within districts with a higher socio-economic status during the first wave.

@@

Social determinants of health are important factors to consider in an epidemiological framework of a pandemic disease like COVID-19. To account for this problem, we included several socio-economic confounders that were available on a district level in Germany. While our analysis is not an exhaustive analysis of the effects of social determinants on COVID-19 infections, we emphasize the necessity of their inclusion and our results add to the growing body of evidence that these factors interact with each other and cluster especially among people or within areas of underprivileged conditions, with detrimental effects on population health \cite{solar2010conceptual}.
